Stepwise Multiple Regressions

### 2021-02-10 Stepwise Multiple Regressions.Rmd
A few different attempts to plot probabilty but neither are currently working

@@

>>>>

```{r}

#Custom function that finds factors with only 1 level
#Source: https://stackoverflow.com/questions/44200195/how-to-debug-contrasts-can-be-applied-only-to-factors-with-2-or-more-levels-er

debug_contr_error <- function (dat, subset_vec = NULL) {
  if (!is.null(subset_vec)) {
    ## step 0
    if (mode(subset_vec) == "logical") {
      if (length(subset_vec) != nrow(dat)) {
        stop("'logical' `subset_vec` provided but length does not match `nrow(dat)`")
        }
      subset_log_vec <- subset_vec
      } else if (mode(subset_vec) == "numeric") {
      ## check range
      ran <- range(subset_vec)
      if (ran[1] < 1 || ran[2] > nrow(dat)) {
        stop("'numeric' `subset_vec` provided but values are out of bound")
        } else {
        subset_log_vec <- logical(nrow(dat))
        subset_log_vec[as.integer(subset_vec)] <- TRUE
        } 
      } else {
      stop("`subset_vec` must be either 'logical' or 'numeric'")
      }
    dat <- base::subset(dat, subset = subset_log_vec)
    } else {
    ## step 1
    dat <- stats::na.omit(dat)
    }
  if (nrow(dat) == 0L) warning("no complete cases")
  ## step 2
  var_mode <- sapply(dat, mode)
  if (any(var_mode %in% c("complex", "raw"))) stop("complex or raw not allowed!")
  var_class <- sapply(dat, class)
  if (any(var_mode[var_class == "AsIs"] %in% c("logical", "character"))) {
    stop("matrix variables with 'AsIs' class must be 'numeric'")
    }
  ind1 <- which(var_mode %in% c("logical", "character"))
  dat[ind1] <- lapply(dat[ind1], as.factor)
  ## step 3
  fctr <- which(sapply(dat, is.factor))
  if (length(fctr) == 0L) warning("no factor variables to summary")
  ind2 <- if (length(ind1) > 0L) fctr[-ind1] else fctr
  dat[ind2] <- lapply(dat[ind2], base::droplevels.factor)
  ## step 4
  lev <- lapply(dat[fctr], base::levels.default)
  nl <- lengths(lev)
  ## return
  list(nlevels = nl, levels = lev)
  }

@@

#Check for single level factors
debug_contr_error(aoc_setup_select_1)

#Remove polymer and shape because they only have one level
aoc_setup_select_1 <- aoc_setup_select %>% 
  dplyr::select(
    `log10(dose.particles.mL.master)`, 
    `log10(dose.mg.L.master)`,
    `log10(dose.um3.mL.master)`,
    `log10(size.length.um.used.for.conversions)`, 
    size_f,     
    # poly_f, 
    # shape_f,
    org_f,
    life_f,
    bio_f,
    `log10(exposure.duration.d)`,
    acute.chronic_f,
    charge_f,
    zetapotential.mV,
    particle_source_f,
    effect_f)

#Omit missing data before modeling
aoc_setup_select_1 <- na.omit(aoc_setup_select_1)

#Fit the full model
Full_Model <- lm(as.numeric(effect_f) ~., data = aoc_setup_select_1)

summary(Full_Model)
```

#Code adapted from: https://stackoverflow.com/questions/36942443/plotting-a-multiple-logistic-regression-for-binary-and-continuous-values-in-r

#Predict probabilities based on model
aoc_setup_select_1$prob = predict(Full_Model, aoc_setup_select_1, type="response")

#Plot probabilities
test_plot <- aoc_setup_select_1 %>% 
  ggplot(aes(x = `log10(size.length.um.used.for.conversions)`, y = prob))+
  geom_point() +
  stat_smooth(method = "glm") #This doesn't use the model so I should probably get rid of it

plot(test_plot)
```

```{r}

#https://blogs.uoregon.edu/rclub/2016/04/05/plotting-your-logistic-regression-models/

Full_Model$coefficients

b0 <- Full_Model$coefficients[1]
dose_counts <- Full_Model$coefficients[2]
dose_mass <- Full_Model$coefficients[3]
dose_vol <- Full_Model$coefficients[4]
size_con <- Full_Model$coefficients[5]
size_100nm_1um <- Full_Model$coefficients[6]
size_1um_100um <- Full_Model$coefficients[7]
org_bacterium <- Full_Model$coefficients[8]
org_crutacea <- Full_Model$coefficients[9]
org_echinoderm <- Full_Model$coefficients[10]
org_fish <- Full_Model$coefficients[11]
org_mollusc <- Full_Model$coefficients[12]
org_nematode <- Full_Model$coefficients[13]
life_early <- Full_Model$coefficients[14]
life_juv <- Full_Model$coefficients[15]
bio_organism <- Full_Model$coefficients[17]
bio_subcell <- Full_Model$coefficients[18]
bio_tissue <- Full_Model$coefficients[19]
exp_dur <- Full_Model$coefficients[20]
acute_chronic <- Full_Model$coefficients[21]
charge_positive <- Full_Model$coefficients[23]
zeta <- Full_Model$coefficients[24]
source_lab <- Full_Model$coefficients[25]

#Set range for x axis variable

X1_range <- seq(from=min(aoc_setup_select_1$`log10(size.length.um.used.for.conversions)`), to=max(aoc_setup_select_1$`log10(size.length.um.used.for.conversions)`), by=.01)

#Not sure what to do here because I'm not running interactions?
logits <- b0 +
  size_con*X1_range +
  dose_counts +
  dose_mass +
  dose_vol +
  size_100nm_1um +
  size_1um_100um +
  org_bacterium +
  org_crutacea +
  org_echinoderm +
  org_fish +
  org_mollusc +
  org_nematode +
  life_early +
  life_juv +
  bio_organism +
  bio_subcell +
  bio_tissue +
  exp_dur +
  acute_chronic +
  charge_positive +
  zeta +
  source_lab

# Compute the probibilities (this is what will actually get plotted):
a_probs <- exp(logits)/(1 + exp(logits))

#plot
plot(X1_range, a_probs, 
     ylim=c(0,1),
     type="l", 
     lwd=3, 
     lty=2, 
     col="gold", 
     xlab="X1", ylab="P(effect)", main="Probability of Effect")
